Title

### 2013-03-26 inc/model_results/lens_charge/lens_charge.tex
added some content, but also restructured some of the folders related to hardware
lens_charge is now all four permutations of long/short oblate/prolate

\subsection{Space-charge Effects in Magnetic Lenses}

@@

In the preceding sections it has already been established that prolate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that prolate pulses will also have markedly better performance.
Therefore, in the sake of simplicity, only the prolate case will be demonstrated here.
For more information see reference \cite{berger_semi-analytic_2010}.

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_lens_charge_long}
      \input{lens_60mm}
    }
    \subfloat[][] { 
      \label{fig:focus_lens_charge_short}
      \input{lens_6mm}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    Pulses begin at the lens' front focal plane with HW1/eM width $ 500 \mu \text{m}$ and duration 500 fs at 20 kV velocity ($c/3$) for an ellipticiy $ \xi ( 0 ) = 0.1 $ (prolate).
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth, \subref{fig:focus_lens_charge_long} $f = $ 60mm and \subref{fig:focus_lens_charge_short} $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
  }
  \label{fig:focus_lens_charge}
\end{figure}

>>>>

\subsection{Space-charge Effects in Magnetic Lenses} \label{sec:mag_lens_charge}

@@

In the preceding sections it has already been established that prolate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that prolate pulses will also have markedly better performance.

\input{lens_charge_plot}
